Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd

# Plot checks for Model
pp_check(bay_model)
plot(bay_model, pars = "(Intercept)", prob = 0.95)
modelsummary::modelsummary(
  list(
    "First model" = bay_model
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-ppcheck
#| fig-cap: "Posterior predictive check of model"

# Plot checks for Model
pp_check(bay_model)

In @fig-ppcheck, we check the Posterior predictive check of model of our model. Since the raw data aligns closely with our prdictions, our model is a good predicton of the data.
